---
title: "Analysis and Visualization"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_bw() + theme(legend.position = "bottom"))

```


```{r}
clean_bee_data = read_csv("./data/clean_bee_data.csv")

# honey bee population for country by year
clean_bee_data %>%
   mutate(year = as.numeric(year)) %>%
   group_by(year) %>%
   summarise(n = sum(honey_producing_colonies)) %>%
   ggplot(aes(x = year, y = n)) + 
   geom_point() +
   geom_line() +
   theme(axis.text.x = element_text(angle = 90)) +
   labs(
     title = "Honey Bee Colony Count in the US",
     x = "Year",
     y = "Honey Bee Colonies Across the US") +
   scale_x_continuous(
      breaks = c(2002, 2007, 2012, 2017))+
   gganimate::transition_reveal(year)
```

```{r}
bee_county = read_csv("./data/bee_county.csv")

bee_county %>%
   mutate(colony_count = as.numeric(colony_count)) %>%
   drop_na(colony_count) %>%
   group_by(year) %>%
   summarise(n = sum(colony_count)) %>%
   ggplot(aes(x = year, y = n)) + 
   geom_point() + 
   geom_line() +
     theme(axis.text.x = element_text(angle = 90)) +
   labs(
     title = "Bee Colony Count in the US",
      x = "Year",
     y = "Bee Colonies Across the US") + 
   scale_x_continuous(
      breaks = c(2002, 2007, 2012)) +
   gganimate::transition_reveal(year)
```

```{r}
top_pesticides = read_csv("./data/top_pesticides.csv")

top_pesticides %>%
  group_by(compound, year) %>%
   na.omit(epest_high_kg) %>%
   summarise(n = sum(epest_high_kg)) %>%
   ggplot(aes(x = year, y = n, color = compound)) + 
   geom_point() + 
   geom_smooth(se = FALSE) +
     theme(axis.text.x = element_text(angle = 90)) +
     labs(
     title = "Pesticide Use in the US",
     x = "Year",
     y = "Weight of Pesticide used in the US (kg)"
   )

```

```{r}
# high range of pesticide use
 top_pesticides %>%
   group_by(year) %>%
   na.omit(epest_high_kg) %>%
   summarise(n = sum(epest_high_kg)) %>%
   ggplot(aes(x = year, y = n)) + 
   geom_point() + 
   geom_smooth(se = FALSE) +
     theme(axis.text.x = element_text(angle = 90)) +
    theme(axis.text.x = element_text(angle = 90)) +
       labs(
     title = "Pesticide Use in the US",
     x = "Year",
     y = "Weight of Pesticide used in the US (kg)"
   )

 #low range of pesticide use
 top_pesticides %>%
   group_by(year) %>%
   na.omit(epest_low_kg) %>%
   summarise(n = sum(epest_low_kg)) %>%
   ggplot(aes(x = year, y = n)) + 
   geom_point() + 
   geom_smooth(se = FALSE) +
     theme(axis.text.x = element_text(angle = 90)) +
     theme(axis.text.x = element_text(angle = 90)) +
       labs(
     title = "Pesticide Use in the US",
     x = "Year",
     y = "Weight of Pesticide used in the US (kg)"
   )
```


```{r}
#library(maps)

#map(database = "United States")

```

```{r}
#library(choroplethr)
#library(choroplethrAdmin1)

#get_admin1_regions("united states of america")

```


# state and pesticide in one graph

merged_state_data %>%
  mutate(year = as.numeric(year.x)) %>%
  group_by(year, compound) %>%
  summarise(colonies = sum(honey_producing_colonies), 
            pesticides = sum(high)) %>%
  ggplot(aes(x = year, y = pesticides, color = compound)) + 
  geom_point() + 
  geom_smooth(se = FALSE) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    title = "Honey Bee Colony Count in the US",
    x = "Year",
    y = "Honey Bee Colonies Across the US")




```{r state honey production colonies}
library(choroplethrMaps)
data(state.map)

state.map = 
  state.map %>%
  filter(region != "alaska", region != "hawaii")

merged_state_data = read_csv("./data/merged_state_data.csv")

merged_state_data_map =
  merged_state_data %>%
  mutate(state = str_to_lower(state)) %>%
  rename(region = state)

state_map_data = left_join(state.map, merged_state_data_map, by = "region")

honey_bee_colony_map = 
  ggplot(state_map_data, aes(long, lat, group = group, fill = honey_producing_colonies)) + geom_polygon(color = "black") + theme_void() + labs(title = "Honey Producing Colonies") + coord_map(projection = "bonne", lat0 = 50) + theme(plot.title = element_text(hjust = 0.5))

honey_bee_colony_map
```

```{r state chlorpyrifos use}
state_chlorpyrifos =
  merged_state_data %>%
  mutate(state = str_to_lower(state)) %>%
  rename(region = state) %>%
  filter(compound == "CHLORPYRIFOS")

state_map_chlorpyrifos = left_join(state.map, state_chlorpyrifos, by = "region") 

chlorpyrifos_map =
  ggplot(state_map_chlorpyrifos, aes(long, lat, group = group, fill = high)) + geom_polygon(color = "black") + theme_void() + labs(title = "Chlorpyrifos") +  coord_map(projection = "bonne", lat0 = 50) + theme(plot.title = element_text(hjust = 0.5))

chlorpyrifos_map
```