---
title: "Gun Violence"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source_code: embed
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(plotly)
library(tidyverse)

# read merged data
merged_data <- read_csv("./data/merged_data.csv") %>%
	filter(year > 2000, year < 2017) %>%
	# fill NAs with data from year 2013
	mutate(year = paste("year", year, sep = "_")) %>%
	spread(key = year, value = Statistics) %>%
	gather(key = selected_years, value = to_fill, year_2001:year_2012, year_2015) %>%
	mutate(to_fill = if_else(is.na(to_fill), year_2016, to_fill)) %>%
	spread(key = selected_years, value = to_fill) %>% 
	gather(key = year, value = Statistics, year_2013:year_2015) %>%
	mutate(year = as.numeric(str_extract(year, "[0-9]{4}")))


# for barplot
firearm_mortality = read_csv("./devon_data/cdc_firearm_mortality_data.csv", na = "Unreliable") %>% 
	janitor::clean_names() %>% 
	select(-ten_year_age_groups_code, -injury_mechanism_all_other_leading_causes_code, -race_code, death_cause = injury_mechanism_all_other_leading_causes) %>% 
	mutate(ten_year_age_groups = factor(ten_year_age_groups, levels = c("1-4 years", "5-14 years", "15-24 years", "25-34 years", "35-44 years", "45-54 years", "55-64 years", "65-74 years", "75-84 years", "85+ years")))


```

Crude Death Rate Map
===================================== 

Column {.sidebar}
-----------------------------------------------------------------------


```{r for_sidebar}

# entries to select from
type_variable <- (merged_data %>% distinct(type_variable) %>% pull())
year <- c(2001:2016)

# year select box 
selectInput("year_1", label = h3("Choose year"),
						choices = as.list(year),
						selected = 2016)

# law strength select box
selectInput("variable_type", label = h3("Choose variable"),
						choices = type_variable, selected = "Crude Rate")
```



(See description page for more information.)

Column {.tabset}
-----------------------------------------------------------------------

### US MAP

```{r us_map}
# for convert state abbreviations to state names
state_abb <- state.name
names(state_abb) <- state.abb

# plot_geo
renderPlotly({
	# map plot setting
	geo1 <- list(
	scope = "usa",
	projection = list(type = "state"),
	showlakes = TRUE,
	lakecolor = toRGB("white")
	)
	
	# display value using color intensity
	merged_data %>% 
	filter(type_variable == input$variable_type, year == input$year_1) %>% 
	plot_geo(locationmode = "USA-states") %>% 
	add_trace(
		z = ~Statistics,
		locations = ~state,
		color = ~Statistics,
		colors = "Reds",
		# add text
		text = ~paste(type_variable, state_abb[state], sep = "")
		) %>%
	layout(
		geo = geo1,
		title = "US Map - State Statistics",
		legend = list(x = 100, y = 0.5)
	)
})

# rsconnect::deployApp("./zanis_shiny.Rmd")

```

### Description

The Crude Death Rate map allows users to toggle between different years (2001-2016), demonstrating the changes in variables over time and visualize regional differences across the U.S. The map includes visualization of distributions of the following variables: unemployment rate, crude rate, deaths, population, law strength (2016 only), smoking, disability, self reported health, drinking, leisure physical activities, overweight, poverty, diabetes, mental health, and sleep. The map demonstrates that there are significant changes over time in all variables.

**Crude Rate:**
Firearm Mortality Rate (number of deaths per 100,000), 2001-2016.

**Death:**
Number of firearm caused deaths each state each year, 2001-2016.

**Sleep:**
Darker means better sleep quality, 2013, 2014, 2016.

**Mental Health:**
The darker the worse mental healthness, 2011-2016.

**Leisure Physical Activities:**
The darker the longer leisure activities, 2011-2016.

**Self Reported Health:**
The darker the better self-rated health, 2011-2016.

**Law Strength:**
The darker the higher law strength, 2016 only.

**Other variables:** The darker the higher in number / higher in rate / more severe in conditions, 2011-2016.

**All missing values are filled with data from year 2016.**



Death by Age and Race
===================================== 

Column {.sidebar}
-----------------------------------------------------------------------

```{r for_sidebar_2}
# years to choose from
selectInput("year_2", label = h3("Choose year"),
						choices = as.list(year), selected = 2013)
```

Column {.tabset}
-----------------------------------------------------------------------

### Crude Firearm Death Rate Across All States by Age Group and Race

```{r barplot_age_race}

# plot barplot
renderPlotly({
  age_race <- firearm_mortality %>% 
  filter(year == input$year_2) %>% 
	group_by(ten_year_age_groups, race) %>%
	summarize(n_deaths = sum(deaths),
						n_population = sum(population)) %>% 
  # normalization
	mutate(crude_rate = (n_deaths/n_population) * 100000) %>% 
  spread(key = race, value = crude_rate) %>%
  janitor::clean_names() %>% 
  # barplot
  plot_ly(x = ~ten_year_age_groups,
  				y = ~white,
  				name = "White",
  				type = "bar") %>% 
  	# stack race one by one
  	add_trace(y = ~black_or_african_american,
  						name = "Black or African American") %>%
  	add_trace(y = ~asian_or_pacific_islander,
  						name = "Asian or Pacific Islander") %>% 
  	add_trace(y = ~american_indian_or_alaska_native,
  						name = "American Indian or Alaska Native") %>% 
  	# add description
  	layout(barmode = "stack",
  				 xaxis = list(title = "Age Groups"),
  				 yaxis = list(title = "Crude Firearm Death Rate")
  				 )

})

```

### Description

This barplot displays the distribution of firearm mortality deaths by age group and race. Visualizing a breakdown of mortality across different age groups and races is important to identify potential disparities in mortality and identify which groups should be the focus of public health interventions.

The plot shows that distributions of deaths across age groups and races changes over time. In 2016, the 15-24 age group had the most firearm-related deaths, mostly concentrated in Black/African American group. Over time, white victims comprised a fairly steady number of deaths across all age groups. A comparison of 2000 versus 2016 reveals that deaths among "American Indian or Alaska Natives" have increased across all age groups. Death rates for Asian/Pacific Islanders have consistently been the lowest across all race groups.

Note that "Hispanic origin" is considered a separate variable from "Race" in the Census data, and therefore was not included in this barchart. The Hispanic origin variable is assessed separately after Race is designated, and therefore individuals identifying as any of the race options included can also choose to select Hispanic/Latino origin. Therefore there is overlap between the two measures.


