---
title: "**Motivation & Related Work**" 
---
<br>

```{r, echo=FALSE, results='hide', message=FALSE}
library(tidyverse)
library(viridis)
library(ggplot2)
library(gganimate)
library(geojsonio)
library(RColorBrewer)
library(rgdal)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_bw() + theme(legend.position = "bottom"))
knitr::opts_chunk$set(echo = TRUE)
```

<br>
```{r, echo=FALSE, results='hide', message=FALSE}

spdf <- geojson_read("data/us_states_hexgrid.geojson",  what = "sp")

# Bit of reformating
spdf@data = spdf@data %>%
  mutate(google_name = gsub(" \\(United States\\)", "", google_name))


```

```{r, echo=FALSE, results='hide', message = FALSE}
library(broom)
spdf@data = spdf@data %>% mutate(google_name = gsub(" \\(United States\\)", "", google_name))
spdf_fortified <- tidy(spdf, region = "google_name")

# Calculate the centroid of each hexagon to add the label:
library(rgeos)
centers <- cbind.data.frame(data.frame(gCentroid(spdf, byid=TRUE), id=spdf@data$iso3166_2))
 
# Now I can plot this shape easily as described before:
ggplot() +
  geom_polygon(data = spdf_fortified, aes( x = long, y = lat, group = group), fill="skyblue", color="white") +
  geom_text(data=centers, aes(x=x, y=y, label=id)) +
  theme_void() +
  coord_map()
```


Bee colony decline has made headlines in recent news reports. The decrease in bee survival has been linked to a decrease in crop diversity, loss of habitat, poor beekeeping practices, as well as widespread and intensive use of pesticides such as neonicotinoids. As a group, we were interested in trends between pesticide use and bee populations. 

One in every three bites of food consumed worldwide depends on pollinators, especially bees, for a successful harvest. In recent years, states like California have seen the effects of a declining bee population in almond harvest. Almond groves that were once bountiful are now sparse in produce, a trend that might forshadow a widespread decrease in food production if decimation of bee colonies continues. 

For much of the past 10 years, beekeepers, primarily in the United States and Europe, have been reporting annual hive losses of 30 percent or higher, substantially more than is considered normal or sustainable. But this winter, many U.S. beekeepers experienced losses of 40 to 50 percent. These numbers were reported right before commercial bee operations prepared to transport their hives for the country’s largest pollinator event: the fertilizing of California’s almond trees. 

Spread across 800,000 acres, California’s almond orchards typically require 1.6 million domesticated bee colonies to pollinate the flowering trees and produce what has become the state’s largest overseas agricultural export. Given the widespread bee loss to so-called “colony collapse disorder” this winter, California’s almond growers were able to pollinate their crop only through an intense, nationwide push to cobble together the necessary number of healthy bee colonies.

If the bee population continues to decline, biodiversity of plants across the country will also decrease. This reduction in bees and plants has the potential to catastrophically impact our food supply.

<br>


# **Related Work**

<br>
One group that is playing an important role in bee management and data driven information disemination, is [BeeInformed](https://beeinformed.org/). Their website includes a dynamic method of tracking bee colony loss across the U.S. for all seasons in an effort to remove the guesswork from bee management. The interactivity aspect of their website was inspiring for this project and motivated our group to try and create a similar layout.


<br>