---
title: "Pesticides_Data"
author: "Maya Spaur"
date: "11/14/2019"
output: github_document
---

This document is to check to see if our pesticides of interest are in the dataset. 


#FINDINGS: 
All 6 pesticides, "CHLOROTHALONIL","CHLORPYRIFOS"   "CLOTHIANIDIN", "FIPRONIL","IMIDACLOPRID",and "THIACLOPRID" have data from 2004-2016. 
Only 4 pesticides, "CHLOROTHALONIL","CHLORPYRIFOS", "FIPRONIL","IMIDACLOPRID" had data from 2002-2003.

```{r setup}
library(tidyverse)
library(viridis)
library(readxl)
```

copied from data_processing document:


```{r, pesticide data 2002}

pest_2002 = read_excel("./data/pesticides_csv/EPest.county.estimates.2002.xlsx") %>% 
  janitor::clean_names() %>% 
  mutate(
    state_fips = state_fips_code,
    county_fips = county_fips_code,
    state_county_fips = paste0(state_fips, county_fips),
    epest_low_kg = round(epest_low_kg),
    epest_high_kg = round(epest_high_kg)) %>%
  select(-state_fips_code, -county_fips_code)
    

unique(pull(pest_2002, compound))
  
```



Identifying if pesticides are in the datasets: 

```{r 2002}
pest_2002 = read_excel("./data/pesticides_csv/EPest.county.estimates.2003.xlsx") %>%
  janitor::clean_names() %>% 
  filter(compound == "CHLOROTHALONIL" | compound == "CLOTHIANIDIN"| compound == "CHLORPYRIFOS" | compound == "FIPRONIL" | compound == "IMIDACLOPRID"| compound ==  "THIACLOPRID")

unique(pull(pest_2002, compound))

```

```{r 2003}
pest_2003 = read_excel("./data/pesticides_csv/EPest.county.estimates.2003.xlsx") %>%
  janitor::clean_names() %>% 
  filter(compound == "CHLOROTHALONIL" | compound == "CLOTHIANIDIN"| compound == "CHLORPYRIFOS" | compound == "FIPRONIL" | compound == "IMIDACLOPRID"| compound ==  "THIACLOPRID")

unique(pull(pest_2003, compound))

```



#just change the file name to change the year

```{r 2004}
pest_ = read_excel("./data/pesticides_csv/EPest.county.estimates.2015.xlsx") %>%
  janitor::clean_names() %>% 
  filter(compound == "CHLOROTHALONIL" | compound == "CLOTHIANIDIN"| compound == "CHLORPYRIFOS" | compound == "FIPRONIL" | compound == "IMIDACLOPRID"| compound ==  "THIACLOPRID")

unique(pull(pest_, compound))

```
